Recurrence spike spectra

### 2022-07-14 Manuscript/inter_spike_manuscript.tex
correction to frequency part
add references

Power grids are a large synchronized complex network that modern societies are depend on the stable functionality of them. To maintain the stability of a power grid, the balance between the energy consumption and energy production should be provided. In an AC-power grid, the grid frequency is an observable variable that reflects how well this balance is satisfied. Thereby, the grid frequency and, indeed its variations over the nominal frequency (which is $50$ \si{Hz} in Europe and many parts of the world, or $60$ \si{Hz} in the Americas, Southern Japan and some other
regions) is continuously recorded and monitored by grid operators. For instance, in the case that there is more (less) demand than supply, the grid frequency decreases (increases) form nominal frequency \cite{}.
\\

The frequency variations can include other information, such as the functionality of control systems \cite{}, the effect of fluctuations in
renewable energies (REs) and demands on the grid \cite{} and, moreover, the effect of regular dispatches due to the trading market \cite{}. The latter induce periodic frequency jumps. The frequency trajectory for the Great Britain (GB) grid Continental Europe (CE) grid shown in Fig.~\ref{} demonstrates clear jumps every hour {\color{red} (maybe we should add this figure and one from auto-correlation or $\tau$-RP)}. Moreover, autocorrelation/$\tau$-RP shows the regular peaks every $30$ \si{min} and one hour (see Fig.~\ref{}). These peaks are caused by a mismatch of power
supply and demand \cite{} during dispatches. In most electricity grids the
operation of dispatchable power plants is scheduled in one hour blocks, where additional (shorter) $30$ and $15$ \si{min} intervals
might exist. Hence\\

>>>>

Power grids are a large synchronized complex network that modern societies are depend on the stable functionality of them. To maintain the stability of a power grid, the balance between the energy consumption and energy production should be provided. In an AC-power grid, the grid frequency is an observable variable that reflects how well this balance is satisfied. Thereby, the grid frequency and, indeed its variations over the nominal frequency (which is $50$ \si{Hz} in Europe and many parts of the world, or $60$ \si{Hz} in the Americas, Southern Japan and some other
regions) is continuously recorded and monitored by grid operators. For instance, in the case that there is more (less) demand than supply, the grid frequency decreases (increases) form nominal frequency \cite{kundur1994power}.
\\

The frequency variations can include other information, such as the functionality of control systems \cite{gorjao2020data}, the effect of fluctuations in
renewable energies (REs) and demands on the grid \cite{anvari2020stochastic} and, moreover, the effect of regular dispatches due to the trading market \cite{meyer2020identifying}. The latter induce periodic frequency jumps. The frequency trajectory for the Great Britain (GB) grid Continental Europe (CE) grid shown in Fig.~\ref{} demonstrates clear jumps every hour {\color{red} (maybe we should add this figure and one from auto-correlation or $\tau$-RP)}. Moreover, autocorrelation/$\tau$-RP shows the regular peaks every $30$ \si{min} and one hour (see Fig.~\ref{}). These peaks are caused by a mismatch of power
supply and demand \cite{weissbach2009high} during dispatches. In most electricity grids the
operation of dispatchable power plants is scheduled in one hour blocks, where additional (shorter) $30$ and $15$ \si{min} intervals
might exist. Looking at the frequency spectrum in Fig.~\ref{}, however does not display sharp peaks exactly at $30$ and $60$ \si{min}. \\

{\color{red} Now we should start the story of Inter-spike-spectrum}.
